---
title: "politics team fr analysis"
author: "Laura Sørine Voldgaard"
date: "2025-06-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# hvorfor er pacman fucked altså

# libraries
install.packages("pacman")
library(pacman)

pacman::p_load(tidyverse, dplyr, readxl, patchwork)

pacman::p_load(lme4)
library(lme4)

install.packages("lmerTest")
library(lmerTest)


```

```{r}
getwd()
```


```{r}
# load data
data <- read_excel("data/data.xlsx", sheet = 1)
```

```{r}
# Replace NA values in 'income' with 5
data$income[is.na(data$income)] <- 5

```


*Analysis*

**Overall political ideology**

Controlling for variables gender, income, birth, birth_rg, residence_rg

```{r}
# make sure all variables are numerical
data_long$gender <- as.factor(data_long$gender)
data_long$income <- as.numeric(data_long$income)
data_long$birth <- as.numeric(data_long$birth)
data_long$birth_rg <- as.numeric(data_long$birth_rg)
data_long$residence_rg <- as.numeric(data_long$residence_rg)


```


```{r}
# I think I deleted this but need it to do the mixed effects model
# Assume you have a respondent ID column
data_long <- data %>%
  pivot_longer(cols = c(past_ideology, now_ideology),
               names_to = "time", values_to = "ideology") %>%
  mutate(time = ifelse(time == "past_ideology", 0, 1))
```




```{r}
# mixed effects model
model_controlled <- lmer(
  polarization ~ time + gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = data_long
)

summary(model_controlled)

```


```{r}
model_controlled_null <- lmer(
  polarization ~ gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = data_long
)

anova(model_controlled_null, model_controlled)

```
Significant, yay!





**Party affiliation**



Mixed effects model

```{r}
library(tidyr)
library(dplyr)

# Step 1: Create long-format ideology and polarization data
long_data <- data %>%
  mutate(
    past_polarization = abs(past_ideology - 5.5),
    now_polarization = abs(now_ideology - 5.5)
  ) %>%
  pivot_longer(
    cols = c(past_polarization, now_polarization),
    names_to = "time_point",
    values_to = "polarization"
  ) %>%
  mutate(
    time = ifelse(time_point == "past_polarization", 0, 1),
    now_party_support = as.factor(now_party_support)
  )

```

```{r}
library(lme4)

model_mixed <- lmer(
  polarization ~ time * now_party_support + gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = long_data
)

summary(model_mixed)

```



Comparing party 10 (no support) to all other party affiliations
```{r}
# set binary variable
data$party10_supporter <- ifelse(data$now_party_support == 10, 1, 0)

```

```{r}
long_data <- data %>%
  mutate(
    past_polarization = abs(past_ideology - 5.5),
    now_polarization = abs(now_ideology - 5.5)
  ) %>%
  pivot_longer(
    cols = c(past_polarization, now_polarization),
    names_to = "time_point",
    values_to = "polarization"
  ) %>%
  mutate(
    time = ifelse(time_point == "past_polarization", 0, 1),
    party10_supporter = as.factor(ifelse(now_party_support == 10, 1, 0))  # match with wide data
  )

```


```{r}
library(lme4)

model_party10 <- lmer(
  polarization ~ time * party10_supporter + gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = long_data
)

summary(model_party10)

```







Reproduction of teammate's results: Do people who support different parties differ in how ideologically extreme they are?
```{r}
# compute distance from the ideological midpoint (e.g., 5.5):
data$past_polarization <- abs(data$past_ideology - 5.5)
data$now_polarization  <- abs(data$now_ideology - 5.5)

```


```{r}
# Run One-Way ANOVA Per Time Point. Basically ask "Are there significant differences in polarization between party supporters at each time point?"

# make sure they are factor
data$past_party_support <- as.factor(data$past_party_support)
data$now_party_support  <- as.factor(data$now_party_support)

# november 2024
aov_past <- aov(past_polarization ~ past_party_support, data = data)
summary(aov_past)

# may 2025
aov_now <- aov(now_polarization ~ now_party_support, data = data)
summary(aov_now)


```
Yes, there is.


```{r}

# Post-hoc tests - Tukey HSD
TukeyHSD(aov_past)
TukeyHSD(aov_now)



```

```{r}
levels(data$past_party_support)
levels(data$now_party_support)

```

Past: Tukey shows that party 4 (no support) is significantly lower polarization than supporters of party 1 (Democratic Party) and party 2 (PPP)




```{r}
# Summarize Group Means (for reporting)
library(dplyr)

# Past
data %>%
  group_by(past_party_support) %>%
  summarise(
    mean_past_extremity = mean(past_polarization, na.rm = TRUE),
    sd_past_extremity = sd(past_polarization, na.rm = TRUE)
  )

# Now
data %>%
  group_by(now_party_support) %>%
  summarise(
    mean_now_extremity = mean(now_polarization, na.rm = TRUE),
    sd_now_extremity = sd(now_polarization, na.rm = TRUE)
  )

```






```{r}
# Test Change in Polarization by Party
data$polarization_change <- data$now_polarization - data$past_polarization

aov_change <- aov(polarization_change ~ now_party_support, data = data)
summary(aov_change)

TukeyHSD(aov_change)

```







```{r}
# Define custom colors
custom_colors <- c(
  "Democratic Party" = "blue",            
  "People Power Party" = "red",          
  "Justice Party" = "#F0E442",               
  "New Future Party" = "#56B4E9",            
  "Reform Party" = "#009E73",                
  "Liberty Unification Party" = "#CC79A7",   
  "Progressive Party" = "#999999",           
  "Cho Kuk Innovation Party" = "#E69F00",    
  "Basic Income Party" = "#8DD3C7",          
  "No Party Preference" = "grey",
  "No Party Supported" = "grey"  # to match the name used in your data
)

# Create long format for plotting
data_long_party <- data %>%
  select(id, now_party_support, past_polarization, now_polarization) %>%
  pivot_longer(cols = c(past_polarization, now_polarization),
               names_to = "time", values_to = "polarization") %>%
  mutate(
    time = factor(
      ifelse(time == "past_polarization", "Nov 2024", "May 2025"),
      levels = c("Nov 2024", "May 2025")
    ),
    now_party_support = factor(
      now_party_support,
      levels = c(1, 2, 3, 4, 5, 6, 7),
      labels = c(
        "Democratic Party",
        "People Power Party",
        "Justice Party",
        "Reform Party",
        "Cho Kuk Innovation Party",
        "Basic Income Party",
        "No Party Supported"
      )
    )
  )

# Plot mean polarization by party and time with custom colors
change_polarization_by_party_affiliation_plot <- ggplot(data_long_party, aes(x = time, y = polarization, color = now_party_support, group = now_party_support)) +
  stat_summary(fun = mean, geom = "line") +
  stat_summary(fun = mean, geom = "point") +
  scale_color_manual(values = custom_colors) +
  labs(
    title = "Change in Polarization by Party Support",
    y = "Mean Polarization (distance from ideological midpoint)",
    x = "Time",
    color = "Party Support"
  ) +
  theme_minimal()

change_polarization_by_party_affiliation_plot

```


```{r save plot}
# save plot
ggsave("viz/change_polarization_by_party_affiliation_plot.png", plot = change_polarization_by_party_affiliation_plot, width = 13, height = 9, dpi = 300)  # Save as PNG
```








**Support for Yoon Suk-yeol**


```{r}
# define polarization from midpoint
data$past_yoon_polarization <- abs(data$past_yoon - 3)
data$now_yoon_polarization  <- abs(data$now_yoon - 3)

```

```{r}
# make data_long_yoon
data_long_yoon <- data %>%
  select(id, past_yoon_polarization, now_yoon_polarization) %>%
  pivot_longer(cols = c(past_yoon_polarization, now_yoon_polarization),
               names_to = "time", values_to = "yoon_polarization") %>%
  mutate(time = ifelse(time == "past_yoon_polarization", 0, 1))

```


```{r}
# add control variables to data_long_yoon
data_long_yoon <- data_long_yoon %>%
  left_join(data %>% select(id, gender, income, birth, birth_rg, residence_rg), by = "id")

```


```{r}
# mixed effects model
model_yoon_polarization <- lmer(
  yoon_polarization ~ time + gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = data_long_yoon
)
summary(model_yoon_polarization)

```









**Gender differences**




hmmm working out the gender thing
```{r}
table(data$gender)
```


```{r}
library(dplyr)

# First, label genders for readability
data %>%
  mutate(gender_label = ifelse(gender == 0, "Men", "Women")) %>%
  group_by(gender_label, past_yoon) %>%
  summarise(count = n()) %>%
  arrange(gender_label, past_yoon)

```


```{r}
data %>%
  mutate(gender_label = ifelse(gender == 0, "Men", "Women")) %>%
  group_by(gender_label, now_yoon) %>%
  summarise(count = n()) %>%
  arrange(gender_label, now_yoon)

```




```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

# Define label mapping
support_labels <- c(
  "1" = "Strongly Oppose",
  "2" = "Somewhat Oppose",
  "3" = "Neutral",
  "4" = "Somewhat Support",
  "5" = "Strongly Support"
)

# Prepare percentage data for past support
plot_data_past <- data %>%
  mutate(gender_label = ifelse(gender == 0, "Men", "Women")) %>%
  group_by(gender_label, past_yoon) %>%
  summarise(count = n(), .groups = "drop") %>%
  complete(gender_label, past_yoon = 1:5, fill = list(count = 0)) %>%
  group_by(gender_label) %>%
  mutate(percentage = count / sum(count) * 100)

# Plot with custom colors and tilted x-axis labels
past_yoon_gender_plot <- ggplot(plot_data_past, aes(x = factor(past_yoon), y = percentage, fill = gender_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_discrete(labels = support_labels) +
  scale_fill_manual(values = c("Men" = "darkcyan", "Women" = "darkorange2")) +
  labs(
    title = "Past Support for Yoon (Nov. 2024) by Gender",
    x = "Yoon Support Level",
    y = "Percentage of Respondents (%)",
    fill = "Gender"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))  # Tilt x-axis labels

past_yoon_gender_plot


```


```{r}
library(dplyr)
library(ggplot2)
library(tidyr)

# --- Reuse the same label mapping ------------------------------------------
support_labels <- c(
  "1" = "Strongly Oppose",
  "2" = "Somewhat Oppose",
  "3" = "Neutral",
  "4" = "Somewhat Support",
  "5" = "Strongly Support"
)

# --- Prepare percentage data for current support ---------------------------
plot_data_now <- data %>%
  mutate(gender_label = ifelse(gender == 0, "Men", "Women")) %>%
  group_by(gender_label, now_yoon) %>%
  summarise(count = n(), .groups = "drop") %>%
  complete(gender_label, now_yoon = 1:5, fill = list(count = 0)) %>%
  group_by(gender_label) %>%
  mutate(percentage = count / sum(count) * 100)

# --- Plot ------------------------------------------------------------------
# Plot current support (May 2025) by gender with tilted x-axis labels
now_yoon_gender_plot <- ggplot(plot_data_now, aes(x = factor(now_yoon), y = percentage, fill = gender_label)) +
  geom_bar(stat = "identity", position = "dodge") +
  scale_x_discrete(labels = support_labels) +
  scale_fill_manual(values = c("Men" = "darkcyan", "Women" = "darkorange2")) +
  labs(
    title = "Current Support for Yoon (May 2025) by Gender",
    x = "Yoon Support Level",
    y = "Percentage of Respondents (%)",
    fill = "Gender"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))  # Tilted labels

now_yoon_gender_plot


```



```{r}
# Use coord_cartesian instead of ylim
past_yoon_gender_plot <- past_yoon_gender_plot + coord_cartesian(ylim = c(0, 65))
now_yoon_gender_plot <- now_yoon_gender_plot + coord_cartesian(ylim = c(0, 65))

# Combine them
past_now_yoon_gender_plot <- past_yoon_gender_plot + now_yoon_gender_plot
past_now_yoon_gender_plot

```



```{r save plot}
# save plot
ggsave("viz/past_now_yoon_gender_plot.png", plot = past_now_yoon_gender_plot, width = 12, height = 6, dpi = 300)  # Save as PNG
```






**Gender differences in ideological polarization**
```{r}
library(lme4)
library(lmerTest)  # for p-values
library(dplyr)
library(tidyr)

# 1. Prepare long-format data
data_long_gender <- data %>%
  mutate(past_extremity = abs(past_ideology - 5.5),
         now_extremity = abs(now_ideology - 5.5)) %>%
  select(id, gender, past_extremity, now_extremity) %>%
  pivot_longer(cols = c(past_extremity, now_extremity),
               names_to = "time", values_to = "extremity") %>%
  mutate(time = ifelse(time == "past_extremity", 0, 1))  # 0 = past, 1 = now

# 2. Run mixed effects model
model_gender <- lmer(extremity ~ time * gender + (1 | id), data = data_long_gender)
summary(model_gender)

```



```{r}
model_gender2 <- lmer(extremity ~ time * gender + income + birth + birth_rg + residence_rg + (1 | id))

```

```{r}
library(lmerTest)  # if not already loaded

# Fit the model
model_gender_controls <- lmer(
  extremity ~ time * gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = data_long_gender
)

# View the summary output
summary(model_gender_controls)

```


```{r}
# Add the demographic variables to the long-format data
data_long_gender <- data_long_gender %>%
  left_join(data %>% select(id, income, birth, birth_rg, residence_rg), by = "id")

# Now run the model again
model_gender_controls <- lmer(
  extremity ~ time * gender + income + birth + birth_rg + residence_rg + (1 | id),
  data = data_long_gender
)

# View model output
summary(model_gender_controls)

```



```{r}
data_long_gender$birth_c <- data_long_gender$birth - mean(data_long_gender$birth, na.rm = TRUE)

```

```{r}
model_gender_controls <- lmer(
  extremity ~ time * gender + income + birth_c + birth_rg + residence_rg + (1 | id),
  data = data_long_gender
)
summary(model_gender_controls)

```



