---
title: "Visualizations"
author: "Politics team"
date: "2025-05-19"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# libraries
install.packages("pacman")
library(pacman)

pacman::p_load(tidyverse, dplyr, readxl, patchwork)

```

```{r}
getwd()
```


```{r}
# load data
data <- read_excel("data/data.xlsx", sheet = 1)
```


*Analysis*
We have been instructed to not address assumptions.


**Political Orientation**

Past political orentiation:

```{r past_party_support}
# Ensure numeric
data$past_party_support <- as.numeric(data$past_party_support)

# Define party labels
party_labels <- data.frame(
  past_party_support = 1:10,
  party_name = c(
    "Democratic Party",             # 1 → blue
    "People Power Party",           # 2 → red
    "Justice Party",
    "New Future Party",
    "Reform Party",
    "Liberty Unification Party",
    "Progressive Party",
    "Cho Kuk Innovation Party",
    "Basic Income Party",
    "No Party Supported"
  )
)

# Count respondents per party
party_counts <- data %>%
  filter(!is.na(past_party_support)) %>%
  count(past_party_support) %>%
  right_join(party_labels, by = "past_party_support") %>%
  replace_na(list(n = 0)) %>%
  arrange(past_party_support)

# Calculate percentage
total_respondents <- sum(party_counts$n)
party_counts <- party_counts %>%
  mutate(percentage = (n / total_respondents) * 100)

# Define custom colors (1 = blue, 2 = red, rest distinguishable)
custom_colors <- c(
  "Democratic Party" = "blue",            # Blue
  "People Power Party" = "red",          # Red
  "Justice Party" = "#F0E442",               
  "New Future Party" = "#56B4E9",            
  "Reform Party" = "#009E73",                
  "Liberty Unification Party" = "#CC79A7",   
  "Progressive Party" = "#999999",           
  "Cho Kuk Innovation Party" = "#E69F00",    
  "Basic Income Party" = "#8DD3C7",          
  "No Party Supported" = "grey"           
)

# Plot with percentages on y-axis
past_party_support_plot <- ggplot(party_counts, aes(x = reorder(party_name, past_party_support), y = percentage, fill = party_name)) +
  geom_bar(stat = "identity") +
  labs(title = "Past Party Support (Nov. 2024)",
       x = "Political Party",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  scale_fill_manual(values = custom_colors, name = "Party")

past_party_support_plot


```



```{r past_party_preference}
# Ensure numeric
data$past_party_preference <- as.numeric(data$past_party_preference)

# Define party labels
party_labels <- data.frame(
  past_party_preference = 1:10,
  party_name = c(
    "Democratic Party",             # 1 → blue
    "People Power Party",           # 2 → red
    "Justice Party",
    "New Future Party",
    "Reform Party",
    "Liberty Unification Party",
    "Progressive Party",
    "Cho Kuk Innovation Party",
    "Basic Income Party",
    "No Party Preference"
  )
)

# Ensure numeric type in party_labels for joining
party_labels$past_party_preference <- as.numeric(party_labels$past_party_preference)

# Count respondents per party preference
party_counts <- data %>%
  filter(!is.na(past_party_preference)) %>%
  count(past_party_preference)

# Join counts with party labels (right join keeps all parties)
party_counts <- party_counts %>%
  right_join(party_labels, by = "past_party_preference") %>%
  replace_na(list(n = 0)) %>%
  arrange(past_party_preference)

# Calculate percentages
total_respondents <- sum(party_counts$n)
party_counts <- party_counts %>%
  mutate(percentage = (n / total_respondents) * 100)

# Define custom colors (1 = blue, 2 = red, rest distinguishable)
custom_colors <- c(
  "Democratic Party" = "blue",            # Blue
  "People Power Party" = "red",          # Red
  "Justice Party" = "#F0E442",               
  "New Future Party" = "#56B4E9",            
  "Reform Party" = "#009E73",                
  "Liberty Unification Party" = "#CC79A7",   
  "Progressive Party" = "#999999",           
  "Cho Kuk Innovation Party" = "#E69F00",    
  "Basic Income Party" = "#8DD3C7",          
  "No Party Preference" = "grey"           
)

# Plot with percentages on y-axis
past_party_preference_plot <- ggplot(party_counts, aes(x = reorder(party_name, past_party_preference), y = percentage, fill = party_name)) +
  geom_bar(stat = "identity") +
  labs(title = "Past Party Preference (Nov. 2024)",
       x = "Political Party",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  scale_fill_manual(values = custom_colors, name = "Party")

past_party_preference_plot

```


```{r past_party_support_preference_grid_plot}
# Use coord_cartesian instead of ylim
past_party_support_plot <- past_party_support_plot + coord_cartesian(ylim = c(0, 55))
past_party_preference_plot <- past_party_preference_plot + coord_cartesian(ylim = c(0, 55))

# Combine them
past_party_support_preference_grid_plot <- past_party_support_plot + past_party_preference_plot
past_party_support_preference_grid_plot

```
```{r save plot}
# save plot
ggsave("viz/past_party_support_preference_grid_plot.png", plot = past_party_support_preference_grid_plot, width = 12, height = 5, dpi = 300)  # Save as PNG
```



Current political orientation:

```{r now political support}
# Ensure numeric
data$now_party_support <- as.numeric(data$now_party_support)

# Define party labels
party_labels <- data.frame(
  now_party_support = 1:10,
  party_name = c(
    "Democratic Party",             # 1 → blue
    "People Power Party",           # 2 → red
    "Justice Party",
    "New Future Party",
    "Reform Party",
    "Liberty Unification Party",
    "Progressive Party",
    "Cho Kuk Innovation Party",
    "Basic Income Party",
    "No Party Supported"
  )
)

# Ensure numeric for join
party_labels$now_party_support <- as.numeric(party_labels$now_party_support)

# Count respondents per party support
party_counts <- data %>%
  filter(!is.na(now_party_support)) %>%
  count(now_party_support)

# Join counts with party labels, keep all parties
party_counts <- party_counts %>%
  right_join(party_labels, by = "now_party_support") %>%
  replace_na(list(n = 0)) %>%
  arrange(now_party_support)

# Calculate percentages
total_respondents <- sum(party_counts$n)
party_counts <- party_counts %>%
  mutate(percentage = (n / total_respondents) * 100)

# Define custom colors (1 = blue, 2 = red, rest distinguishable)
custom_colors <- c(
  "Democratic Party" = "blue",            # Blue
  "People Power Party" = "red",            # Red
  "Justice Party" = "#F0E442",               
  "New Future Party" = "#56B4E9",            
  "Reform Party" = "#009E73",                
  "Liberty Unification Party" = "#CC79A7",   
  "Progressive Party" = "#999999",           
  "Cho Kuk Innovation Party" = "#E69F00",    
  "Basic Income Party" = "#8DD3C7",          
  "No Party Supported" = "grey"           
)

# Plot with percentages on y-axis
now_party_support_plot <- ggplot(party_counts, aes(x = reorder(party_name, now_party_support), y = percentage, fill = party_name)) +
  geom_bar(stat = "identity") +
  labs(title = "Current Party Support (May 2025)",
       x = "Political Party",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  scale_fill_manual(values = custom_colors, name = "Party")

now_party_support_plot

```


```{r now political preference}
# Ensure numeric
data$now_party_preference <- as.numeric(data$now_party_preference)

# Define party labels
party_labels <- data.frame(
  now_party_preference = 1:10,
  party_name = c(
    "Democratic Party",             # 1 → blue
    "People Power Party",           # 2 → red
    "Justice Party",
    "New Future Party",
    "Reform Party",
    "Liberty Unification Party",
    "Progressive Party",
    "Cho Kuk Innovation Party",
    "Basic Income Party",
    "No Party Preference"
  )
)

# Ensure numeric for joining
party_labels$now_party_preference <- as.numeric(party_labels$now_party_preference)

# Count respondents per party preference
party_counts <- data %>%
  filter(!is.na(now_party_preference)) %>%
  count(now_party_preference)

# Right join with party labels to keep all parties
party_counts <- party_counts %>%
  right_join(party_labels, by = "now_party_preference") %>%
  replace_na(list(n = 0)) %>%
  arrange(now_party_preference)

# Calculate percentages
total_respondents <- sum(party_counts$n)
party_counts <- party_counts %>%
  mutate(percentage = (n / total_respondents) * 100)

# Define custom colors
custom_colors <- c(
  "Democratic Party" = "blue",            
  "People Power Party" = "red",          
  "Justice Party" = "#F0E442",               
  "New Future Party" = "#56B4E9",            
  "Reform Party" = "#009E73",                
  "Liberty Unification Party" = "#CC79A7",   
  "Progressive Party" = "#999999",           
  "Cho Kuk Innovation Party" = "#E69F00",    
  "Basic Income Party" = "#8DD3C7",          
  "No Party Preference" = "grey"           
)

# Plot with percentage y-axis
now_party_preference_plot <- ggplot(party_counts, aes(x = reorder(party_name, now_party_preference), y = percentage, fill = party_name)) +
  geom_bar(stat = "identity") +
  labs(title = "Current Party Preference (May 2025)",
       x = "Political Party",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(legend.position = "none") +
  scale_fill_manual(values = custom_colors, name = "Party")

now_party_preference_plot

```


```{r grid now political orientation}
# Set common y-axis scale
now_party_support_plot <- now_party_support_plot + coord_cartesian(ylim = c(0, 55))
now_party_preference_plot <- now_party_preference_plot + coord_cartesian(ylim = c(0, 55))

# Combine plots
now_party_support_preference_grid_plot <- now_party_support_plot + now_party_preference_plot
now_party_support_preference_grid_plot

```

```{r save plot}
# save plot
ggsave("viz/now_party_support_preference_grid_plot.png", plot = now_party_support_preference_grid_plot, width = 12, height = 5, dpi = 300)  # Save as PNG
```



**Overall ideology**


```{r past_ideology}
# Ensure numeric
data$past_ideology <- as.numeric(data$past_ideology)

# Count actual responses
past_ideology_counts <- data %>%
  filter(!is.na(past_ideology)) %>%
  count(past_ideology)

# Create full range 1–10
full_range <- tibble(past_ideology = 1:10)

# Left join to fill in missing values with NA, then replace with 0
past_ideology_counts <- full_range %>%
  left_join(past_ideology_counts, by = "past_ideology") %>%
  mutate(n = ifelse(is.na(n), 0, n))

# Calculate percentages
total_respondents <- sum(past_ideology_counts$n)
past_ideology_counts <- past_ideology_counts %>%
  mutate(percentage = (n / total_respondents) * 100)

# Plot with red-to-blue gradient and no legend
past_ideology_plot <- ggplot(past_ideology_counts, aes(x = factor(past_ideology), y = percentage, fill = past_ideology)) +
  geom_col() +
  scale_fill_gradient(low = "red", high = "blue") +
  labs(title = "Past Political Ideology (Nov. 2024)",
       x = "Political Ideology (1 = Conservative, 10 = Progressive)",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(legend.position = "none")

past_ideology_plot

```



```{r now_ideology}
# Ensure numeric
data$now_ideology <- as.numeric(data$now_ideology)

# Count actual responses
now_ideology_counts <- data %>%
  filter(!is.na(now_ideology)) %>%
  count(now_ideology)

# Create full range 1–10
full_range <- tibble(now_ideology = 1:10)

# Left join to fill in missing values with NA, then replace with 0
now_ideology_counts <- full_range %>%
  left_join(now_ideology_counts, by = "now_ideology") %>%
  mutate(n = ifelse(is.na(n), 0, n))

# Calculate percentages
total_respondents <- sum(now_ideology_counts$n)
now_ideology_counts <- now_ideology_counts %>%
  mutate(percentage = (n / total_respondents) * 100)

# Plot with red-to-blue gradient and no legend
now_ideology_plot <- ggplot(now_ideology_counts, aes(x = factor(now_ideology), y = percentage, fill = now_ideology)) +
  geom_col() +
  scale_fill_gradient(low = "red", high = "blue") +
  labs(title = "Current Political Ideology (May 2025)",
       x = "Political Ideology (1 = Conservative, 10 = Progressive)",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(legend.position = "none")

now_ideology_plot

```

```{r past_current_ideology_grid_plot}
# Use coord_cartesian instead of ylim
past_ideology_plot <- past_ideology_plot + coord_cartesian(ylim = c(0, 26))
now_ideology_plot <- now_ideology_plot + coord_cartesian(ylim = c(0, 26))

# Combine them
past_current_ideology_grid_plot <- past_ideology_plot + now_ideology_plot
past_current_ideology_grid_plot

```

```{r save plot}
# save plot
ggsave("viz/past_current_ideology_grid_plot.png", plot = past_current_ideology_grid_plot, width = 12, height = 5, dpi = 300)  # Save as PNG
```



```{r}
# If you haven't already
 install.packages("patchwork")

library(patchwork)

# Set y-axis limits with coord_cartesian
past_ideology_plot <- past_ideology_plot + coord_cartesian(ylim = c(0, 26))
now_ideology_plot  <- now_ideology_plot  + coord_cartesian(ylim = c(0, 26))

# Combine vertically using "/"
past_current_ideology_grid_plot <- past_ideology_plot / now_ideology_plot

# Display
past_current_ideology_grid_plot

```


```{r save plot}
# save plot
ggsave("viz/past_current_ideology_grid_plot2.png", plot = past_current_ideology_grid_plot, width = 8, height = 9, dpi = 300)  # Save as PNG
```






```{r}
data$past_polarization <- abs(data$past_ideology - 5.5)
data$now_polarization  <- abs(data$now_ideology - 5.5)

```

```{r}
t.test(data$now_polarization, data$past_polarization, paired = TRUE)

```






```{r}
# Load required library
library(broom)

# Run the paired t-test
t_test_result <- t.test(data$now_polarization, data$past_polarization, paired = TRUE)

# Tidy the result
t_table <- tidy(t_test_result)

# View it
print(t_table)

```

```{r}
# As CSV
write.csv(t_table, "paired_ttest_polarization.csv", row.names = FALSE)

# Or display nicely in RMarkdown/Quarto
library(knitr)
kable(t_table, caption = "Paired t-test: Change in Political Polarization (Nov 2024 → May 2025)")

```




```{r}
install.packages(c("broom", "gt", "webshot2"))

```


```{r}
library(broom)
library(gt)
library(webshot2)

# Run the paired t-test
t_test_result <- t.test(data$now_polarization, data$past_polarization, paired = TRUE)

# Tidy it into a data frame
t_df <- tidy(t_test_result)

# Optional: Rename columns for clarity
t_df <- t_df %>%
  dplyr::rename(
    `Mean Difference` = estimate,
    `t Statistic` = statistic,
    `p-Value` = p.value,
    `Degrees of Freedom` = parameter,
    `CI Lower` = conf.low,
    `CI Upper` = conf.high,
    `Test Type` = method,
    `Alternative Hypothesis` = alternative
  )

# Create and style the table
gt_table <- gt(t_df) %>%
  tab_header(
    title = "Paired t-test: Change in Political Polarization",
    subtitle = "Comparing Nov 2024 and May 2025"
  ) %>%
  fmt_number(columns = where(is.numeric), decimals = 3)

# Save as PNG
gtsave(gt_table, "polarization_ttest.png")

```



























```{r}
library(ggplot2)

# Histogram of changes in polarization
data$polarization_change <- data$now_polarization - data$past_polarization

ggplot(data, aes(x = polarization_change)) +
  geom_histogram(binwidth = 1, fill = "tomato", color = "white") +
  labs(title = "Change in Ideological Polarization",
       x = "Change in Distance from Center (Now - Past)",
       y = "Number of Respondents") +
  theme_minimal()

```






```{r}
library(ggplot2)
library(dplyr)

# Convert to factor if not already
data$after_pol_change <- factor(data$after_pol_change, levels = c(1, 2, 3),
                                labels = c("Yes", "No", "Not Sure"))

# Calculate percentages
change_counts <- data %>%
  filter(!is.na(after_pol_change)) %>%
  count(after_pol_change) %>%
  mutate(percentage = (n / sum(n)) * 100)

# Bar plot
perceived_change_political_views_plot <- ggplot(change_counts, aes(x = after_pol_change, y = percentage, fill = after_pol_change)) +
  geom_bar(stat = "identity") +
  labs(title = "Perceived Change in Political Views",
       x = "Did Your Political Views Change?",
       y = "Percentage of Respondents (%)") +
  scale_fill_manual(values = c("Yes" = "#66c2a5", "No" = "#fc8d62", "Not Sure" = "#8da0cb")) +
  theme_minimal() +
  theme(legend.position = "none")

perceived_change_political_views_plot

```


```{r save plot}
# save plot
ggsave("viz/perceived_change_political_views_plot.png", plot = perceived_change_political_views_plot, width = 10, height = 5, dpi = 300)  # Save as PNG
```


```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(ggforce)

# Ensure numeric
data$past_ideology <- as.numeric(data$past_ideology)
data$now_ideology  <- as.numeric(data$now_ideology)

# Create ideology change type
data <- data %>%
  mutate(
    x1 = 1,
    x2 = 2,
    line_type = ifelse(past_ideology == now_ideology, "No Change", "Changed")
  )

# Create Bezier data including color variable
bezier_data <- data %>%
  select(id, past_ideology, now_ideology, line_type) %>%
  rowwise() %>%
  mutate(color_value = past_ideology) %>%  # You can also try (past_ideology + now_ideology)/2
  do(data.frame(
    id = .$id,
    line_type = .$line_type,
    color_value = .$color_value,
    x = c(1, 1.5, 2),
    y = c(.$past_ideology, mean(c(.$past_ideology, .$now_ideology)), .$now_ideology)
  )) %>%
  ungroup()

# Plot with color gradient
political_ideology_shifts_plot <- ggplot(bezier_data, aes(x = x, y = y, group = id, color = color_value, linetype = line_type)) +
  geom_bezier(alpha = 0.6, size = 0.9) +
  scale_color_gradient(low = "red", high = "blue", name = "Political Ideology") +
  scale_linetype_manual(values = c("Changed" = "solid", "No Change" = "dotted")) +
  scale_x_continuous(breaks = c(1, 2), labels = c("Nov 2024", "May 2025")) +
  labs(
    title = "Shifts in Political Ideology",
    x = "", y = "Political Ideology (1 = Conservative, 10 = Progressive)",
    linetype = "Change in Ideology"
  ) +
  theme_minimal()

political_ideology_shifts_plot

```


```{r save plot}
# save plot
ggsave("viz/political_ideology_shifts_plot.png", plot = political_ideology_shifts_plot, width = 12, height = 8, dpi = 300)  # Save as PNG
```









---------------------------



**Opinion on Yoon**

```{r}
# load data
data <- read_excel("data/data.xlsx", sheet = 1)
```

```{r}
# Replace NA values in 'income' with 5
data$income[is.na(data$income)] <- 5

```



```{r}
library(ggplot2)
library(dplyr)

# Define labels
yoon_labels <- c(
  "1" = "Strongly Oppose",
  "2" = "Somewhat Oppose",
  "3" = "Neutral",
  "4" = "Somewhat Support",
  "5" = "Strongly Support"
)

# Count responses (make sure values are treated as character for labeling)
yoon_counts <- data %>%
  filter(!is.na(past_yoon)) %>%
  count(past_yoon = as.character(past_yoon)) %>%
  complete(past_yoon = as.character(1:5), fill = list(n = 0)) %>%
  mutate(percentage = (n / sum(n)) * 100)

# Custom colors
yoon_colors <- c(
  "Strongly Oppose" = "#D73027",
  "Somewhat Oppose" = "#FC8D59",
  "Neutral" = "#FFFFBF",
  "Somewhat Support" = "#91BFDB",
  "Strongly Support" = "#4575B4"
)

# Plot using labeled versions on x-axis
past_yoon_support_plot <- ggplot(yoon_counts, aes(x = factor(past_yoon, levels = 1:5, labels = yoon_labels), 
                        y = percentage, 
                        fill = factor(past_yoon, levels = 1:5, labels = yoon_labels))) +
  geom_bar(stat = "identity") +
  labs(title = "Past Support for Yoon (Nov. 2024)",
       x = "Yoon Support Level",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  scale_fill_manual(values = yoon_colors)

past_yoon_support_plot

```










```{r}
library(ggplot2)
library(dplyr)

# Define labels
yoon_labels <- c(
  "1" = "Strongly Oppose",
  "2" = "Somewhat Oppose",
  "3" = "Neutral",
  "4" = "Somewhat Support",
  "5" = "Strongly Support"
)

# Count responses (make sure values are treated as character for labeling)
yoon_counts <- data %>%
  filter(!is.na(now_yoon)) %>%
  count(now_yoon = as.character(now_yoon)) %>%
  complete(now_yoon = as.character(1:5), fill = list(n = 0)) %>%
  mutate(percentage = (n / sum(n)) * 100)

# Custom colors
yoon_colors <- c(
  "Strongly Oppose" = "#D73027",
  "Somewhat Oppose" = "#FC8D59",
  "Neutral" = "#FFFFBF",
  "Somewhat Support" = "#91BFDB",
  "Strongly Support" = "#4575B4"
)

# Plot using labeled versions on x-axis
current_yoon_support_plot <- ggplot(yoon_counts, aes(x = factor(now_yoon, levels = 1:5, labels = yoon_labels), 
                        y = percentage, 
                        fill = factor(now_yoon, levels = 1:5, labels = yoon_labels))) +
  geom_bar(stat = "identity") +
  labs(title = "Current Support for Yoon (May 2025)",
       x = "Yoon Support Level",
       y = "Percentage of Respondents (%)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1),
        legend.position = "none") +
  scale_fill_manual(values = yoon_colors)

current_yoon_support_plot
```





```{r past_current_yoon_support_grid_plot}
# Use coord_cartesian instead of ylim
past_yoon_support_plot <- past_yoon_support_plot + coord_cartesian(ylim = c(0, 60))
current_yoon_support_plot <- current_yoon_support_plot + coord_cartesian(ylim = c(0, 60))

# Combine them
past_current_yoon_support_grid_plot <- past_yoon_support_plot + current_yoon_support_plot
past_current_yoon_support_grid_plot

```



```{r save plot}
# save plot
ggsave("viz/past_current_yoon_support_grid_plot.png", plot = past_current_yoon_support_grid_plot, width = 12, height = 5, dpi = 300)  # Save as PNG
```




```{r}
data$past_yoon <- as.numeric(data$past_yoon)
data$now_yoon  <- as.numeric(data$now_yoon)

```



```{r}
# Paired t-test: Did Yoon support change?
yoon_support_ttest <- t.test(data$now_yoon, data$past_yoon, paired = TRUE)

# View result
yoon_support_ttest

```



```{r}
# Make sure both are numeric
data$past_yoon <- as.numeric(data$past_yoon)
data$now_yoon <- as.numeric(data$now_yoon)

# Calculate direction and size of change
data$change_yoon <- data$now_yoon - data$past_yoon

```

```{r}
library(dplyr)

change_summary <- data %>%
  mutate(direction = case_when(
    change_yoon > 0 ~ "More Supportive",
    change_yoon < 0 ~ "Less Supportive",
    change_yoon == 0 ~ "No Change"
  )) %>%
  count(direction) %>%
  mutate(percent = round((n / sum(n)) * 100, 1))

change_summary

```


```{r}
library(ggplot2)

ggplot(change_summary, aes(x = direction, y = percent, fill = direction)) +
  geom_col() +
  geom_text(aes(label = paste0(percent, "%")), vjust = -0.5) +
  labs(title = "Change in Support for President Yoon",
       x = "Direction of Change",
       y = "Percentage of Respondents") +
  theme_minimal() +
  theme(legend.position = "none")

```

```{r}
ggplot(data, aes(x = change_yoon)) +
  geom_histogram(binwidth = 1, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Changes in Yoon Support",
       x = "Change Score (Now - Past)",
       y = "Number of Respondents") +
  theme_minimal()

```





```{r}
data$change_group <- dplyr::case_when(
  data$change_yoon > 0 ~ "More Supportive",
  data$change_yoon < 0 ~ "Less Supportive",
  data$change_yoon == 0 ~ "No Change"
)

anova_model <- aov(hostility_sum ~ change_group, data = data)
summary(anova_model)

```








```{r}
data$change_yoon <- data$now_yoon - data$past_yoon

```

```{r}
# Define midpoint of Yoon scale as 3 (Neutral)
data$past_yoon_polarization <- abs(data$past_yoon - 3)
data$now_yoon_polarization  <- abs(data$now_yoon - 3)

```

```{r}
t.test(data$now_yoon_polarization, data$past_yoon_polarization, paired = TRUE)

```

```{r}
library(broom)
library(gt)
library(webshot2)

# Recalculate polarization around neutrality (3 = Neutral)
data$past_yoon_polarization <- abs(data$past_yoon - 3)
data$now_yoon_polarization  <- abs(data$now_yoon - 3)

# Run paired t-test
t_test_result <- t.test(data$now_yoon_polarization, data$past_yoon_polarization, paired = TRUE)

# Tidy result into data frame
t_df <- tidy(t_test_result)

# Rename columns for clarity
t_df <- t_df %>%
  dplyr::rename(
    `Mean Difference` = estimate,
    `t Statistic` = statistic,
    `p-Value` = p.value,
    `Degrees of Freedom` = parameter,
    `CI Lower` = conf.low,
    `CI Upper` = conf.high,
    `Test Type` = method,
    `Alternative Hypothesis` = alternative
  )

# Create and style table
gt_table <- gt(t_df) %>%
  tab_header(
    title = "Paired t-test: Change in Support Polarization for Yoon",
    subtitle = "Based on deviation from Neutral (Nov 2024 vs. May 2025)"
  ) %>%
  fmt_number(columns = where(is.numeric), decimals = 3)

# Save as PNG
gtsave(gt_table, "yoon_polarization_ttest.png")

```




























-----------------------------------------------------




**Categorical** --> chi-square
assumptions of chi-square: https://www.statology.org/chi-square-test-assumptions/

```{r}
# Install and load the package
#install.packages('dplyr')

#library(dplyr)

# Select the columns of interest
#selected_data <- dataset %>% select(Highest educational level, Anemia level)

# Create a contingency table for Highest educational level and Anemia level
#contingency_table <- table(selected_data$Highest educational level, selected_data$Anemia level)

# View the contingency table
#print(contingency_table)

# Perform chi-square test
#chi_square_test <- chisq.test(contingency_table)

# View the results
#print(chi_square_test)
```

(see slides from class for syntax she wants us to use)











**Continuous** --> t-test/Pearson's R/OLS regression (note: treat likert scale as continuous variable)

assumptions Pearson's R: https://www.scribbr.com/frequently-asked-questions/assumptions-of-pearson-correlation-coefficient/

ols regression: https://www.datacamp.com/tutorial/ols-regression

```{r}

```



we cannot treat dummy variables as continuous variables

















